### 2023-06-01 paper/localpsf.tex
editing numerical results section

@@

\begin{table}
	\centering
	{
%	\setlength{\tabcolsep}{0.1em}
%	\renewcommand{\arraystretch}{2.0}
	\begin{tabular}{cccc}
		  & $T=0.5$ & $T=1.0$ & $T=2.0$ \\
		$\kappa=1.0e{-4}$  & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K1.e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K1.e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K1.e-4.png} \\
		$\kappa=3.2e{-4}$ & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K3.2e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K3.2e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K3.2e-4.png} \\
		$\kappa=1.0e{-3}$ & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K1.e-3.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K1.e-3.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K1.e-3.png}
	\end{tabular}
	}
	\caption{Impulse responses for a variety of different diffusion parameters $\kappa$ and simulation times $T$.}
	\label{tbl:table_of_figures}
\end{table}

\begin{figure}
	\caption{Impulse responses for various diffusivities kappa and fixed simulation time Tf=0.5 (top) and simulation times with fixed $\kappa=1e{-3}$ (bot).}
	\label{fig:adv_vary_kappa_tf}
\end{figure}

@@

\begin{itemize}
	\item Picture of velocity field, initial condition, final condition, reconstruction (1) (OKOK)
	\item Impulse responses: vary time and Peclet number (3) (OKOK)
	\item CG convergence (1) CG iters vs Peclet number (Morozov) (2) (OKOK)
	\item Preconditioned spectrum, condition numbers? (1)
\end{itemize}

>>>>

\begin{table}
	\centering
	{
		%	\setlength{\tabcolsep}{0.1em}
		%	\renewcommand{\arraystretch}{2.0}
		\begin{tabular}{cccc}
			& $T=0.5$ & $T=1.0$ & $T=2.0$ \\
			$\kappa=1.0e{-4}$  & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K1.e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K1.e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K1.e-4.png} \\
			$\kappa=3.2e{-4}$ & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K3.2e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K3.2e-4.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K3.2e-4.png} \\
			$\kappa=1.0e{-3}$ & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T0.5_K1.e-3.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T1.0_K1.e-3.png} & \includegraphics[scale=0.15, valign=c]{impulse_response_P(0.3,0.6)_T2.0_K1.e-3.png}
		\end{tabular}
	}
	\caption{Impulse responses for a variety of different diffusion parameters $\kappa$ and simulation times $T$.}
	\label{tbl:adv_vary_kappa_tf}
\end{table}

@@

@@

%\begin{itemize}
%	\item Picture of velocity field, initial condition, final condition, reconstruction (1) (OKOK)
%	\item Impulse responses: vary time and Peclet number (3) (OKOK)
%	\item CG convergence (1) CG iters vs Peclet number (Morozov) (2) (OKOK)
%	\item Preconditioned spectrum, condition numbers? (1)
%\end{itemize}
